A look into Kamala Harris' polls in the upcoming 2024 US Presidential Election 

### 2024-10-22 paper/paper.qmd
Updated README
Exported models to models subfolder

Imported models to Quarto doc

Updated references and general structure

Small edits to clean_data

Deleted unnecessary files

---
title: "An abundance of invasive trees in Toronto and a lack of trees in the streets of Toronto's core. "
subtitle: ""
author: 
  - Veyasan Ragulan
thanks: "Code and data are available at: https://github.com/Veyasan1/2024USElectionModel"
date: today
date-format: long
abstract: "Tree- lined streets are an exceptional way to add nature to urban envirnoments. Using the Street Tree data from OpenData Toronto, this paper examines the patterns and trends in Toronto's street trees. Tree species count, count of trees by ward, and distribution of tree-diameters were analysed. Uncovered was a abundance of a non-native tree species, and a lack of trees on the streets of Toronto's core"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

@@

The data used in this model comes from fivethirtyeight.com, a polling site known for their in-depth analysis and data on US elections. Here, we have used the 2024 general election data, originally accessed on 10/21/2024. The data contains information from several polls taken across the United States, including the operator, sponsors, methodology, a numeric grade to quanitfy the quality of the poll, and when and where the poll was taken. From this dataset, polls predicting a Harris win were considered, to construct the predictive model.

@@

## The worrying prominence of Acer platanoides

## The lack of trees in Toronto-Centre

## Anomalies in DBH diameters and potential causes

@@

## Data Cleaning

>>>>

---
title: "A look into Kamala Harris' polls in the upcoming 2024 US Presidential Election "
subtitle: ""
author: 
  - Veyasan Ragulan
thanks: "Code and data are available at: https://github.com/Veyasan1/2024USElectionModel"
date: today
date-format: long
abstract: "The 2024 US election has been seen as a close race between the Democratic nominess Kamala Harris, and the Republican Nominee Donald Trump, with each candidate holding down key states and matching each other in battleground states such as Pennsylvania and Georgia. This paper looks at the polling as of late October 2024 to see how Kamala Harris fares as the election draws near."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)

library(rstanarm)

bayesian_model <-
  readRDS(file = here::here("models/electionmodel.rds"))

spline_model <- 
  readRDS(file = here::here("models/splinemodel.rds"))
```

@@

This report was written with the assistance of R @citeR. Additionally, @tidyverse, and @rstanarm were used to clean the data, write models, and analyse results. The structure of this report heeds Rohan Alexander's example @tellingstories.

@@

The data used in this model comes from fivethirtyeight.com, a polling site known for their in-depth analysis and data on US elections @fivethirtyeight. Here, we have used the 2024 general election data, originally accessed on 10/21/2024. The data contains information from several polls taken across the United States, including the operator, sponsors, methodology, a numeric grade to quanitfy the quality of the poll, and when and where the poll was taken. From this dataset, polls predicting a Harris win were considered, to construct the predictive model.

@@

## Trends from pollsters

## Trends from states

## Trends from sponsors

## Trends from methodology

@@

## Pollster Analysis

## Poll Blueprint
